Formalizing Stack Safety as a Security Property\ifcameraready\else\vspace{-0.75cm}\fi

### 2023-05-11 submission5/core.tex
Discussing Nick and Andre

>>>>

\paragraph*{Lazy Applicability}

Roessler and DeHon describe {\em Lazy Tagging and Clearing} as aiming to enforce
a fundamentally different property than {\em Depth Isolation}. They consider \(DI\)
a form of memory safety, while they claim that {\em dataflow integrity} enforces a
form of {\em dataflow integrity}. Because our properties are phrased in
terms of dataflow, they represent a plausible definition  against which \(LTC\) can be tested.
